---
title: "Week 3 Discussion File"
author: "Allison Horst"
date: "1/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Part A: Make edits to main that conflict with existing

In this section, you will work in a branch to make updates that conflict with the version of code that are in the main branch. 

- Make a new branch called yourname-branch
- Make sure you are working in the code chunk below that refers to YOUR partner number. 
- Follow the commented instructions in your chunk to make edits in your branch, then push changes to your upstream remote branch

```{r partner_1a}
# Partner 1: 
# Run the code below to see the original graph
# Change the code below to make the point color change based on 'cut', and update the theme to theme_bw()

ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point(aes(color = cut)) +
  theme_bw()
```

```{r partner_2a}
# Partner 2: 
# Run the code below to see the original graph
# Change the code below to make the geom a geom_jitter, and update the theme to theme_light. 

ggplot(data = diamonds, aes(x = color, y = carat)) +
  geom_jitter() +
  theme_dark()
```

